\documentclass[letter,12pt]{article}
\usepackage[margin=2.3cm]{geometry}
\usepackage{parskip}
\usepackage{amsthm}
\begin{document}
Name: Yan, Zi \\
Course: CIS 502 \\
Assignment: HW8 \\
\line(1,0){400}
%Write your content here
\section*{Question 1}
The algorithm is for each node $v$ and its left child $v'$ and right child $v''$,
if $l_{(v,v')} \neq l_{(v, v'')}$, then adjust the lengths of two edges such that
let $l_{(v,v')} = l_{(v, v'')} = \max\{l_{(v,v')}, l_{(v, v'')}\}$. After we visit each node
by using BFS and adjust corresponding edges, the resulting binary tree has
zero skew and the total edge length is as small as possible.

Observation 1: For any subtree rooted at $v$ with all its descendent leaves, $x_1$ to 
$x_k$, after we make every path from $v$ to $x_i$, where $i \in [1..k]$, equal, there 
always is a path from $v$ to a leaf $x_m$, none of whose edges will be increased, for
the case that the total length is as small as possible,
\begin{proof}
Suppose not. Let $l_i$ denote the length of the path from $v$ to $x_i$, where $i \in 
[1..k]$. Suppose we add $\Delta_i>0$ to each path from $v$ to $x_i$, such that all 
$l_i+\Delta_i$ are equal and the total length is as small as possible. But we can find the 
smallest $\Delta_m0$ and subtract $\Delta_m$ from each $\Delta_i$, such that for 
each path from $v$ to $x_i$, $(l_i+\Delta_i-\Delta_m)$ is still equal to each other and 
get the a smaller total length. Additionally, because $\Delta_m = 0$, the path from 
$v$ to $x_m$ is untouched, therefore no edges along the path from $v$ to $x_m$ is 
increased. 
\end{proof}
\begin{proof}
Suppose not. Then there are other solutions better than the algorithm provided.
Let $v$ be any node that do not follow the above algorithm.
There are three alternate solutions that can be better, 
\begin{itemize}
    \item[1)] we let $l_{(v,v')} = l_{(v, v'')} = l' >  \max\{l_{(v,v')}, l_{(v, v'')}\}$. Then at
    node $v$, all paths from $v$ are increased, which contradicts the observation 1.
    \item[2)] we let $l_{(v,v')} > l_{(v, v'')}$ after we change the lengths of the 
    corresponding edges. Therefore, the length of each path from $v''$ to a leaf has to 
    be increased by $l_{(v,v')} - l_{(v, v'')}$, in order to keep zero skew from root to 
    leaves. Then all paths from $v''$ are increased, which contradicts the observation 1.
    \item[3)] we let $l_{(v,v')} < l_{(v, v'')}$ after we change the lengths of the 
    corresponding edges. Symmetrically, we will get a contradiction.
\end{itemize}
In sum, any alternate solution is no better than the provided one. So the provided
algorithm is optimal.
\end{proof}

The BFS takes $O(n)$ for the tree traverse, and at each node the operation is constant
time, therefore, the total runtime is $O(n)$.

\section*{Question 2}
First, we make all weights of X-edges larger than Y-edges, and use Prim's algorithm
to find a minimum spanning $T_1$ with least number of X-edges $x_{min}$. Second, 
we make all weights of X-edges smaller than Y-edges, and use Prim's algorithm to find 
a minimum spanning tree $T_2$ with largest number of X-edges $x_{max}$.

If $k < x_{min}$ or $k>x_{max}$, we can conclude that no such tree that with exactly 
$k$ edges labeled $X$ exists. If $k = x_{min} = x_{max}$, then the minimum spanning 
tree produced above is the spanning tree with exactly $k$ edges labeled $X$. For the
case that $x_{min} < k < x_{max}$, we need to find a tree with exactly $k$ edges 
labeled $X$ by swapping some edges of the minimum spanning tree, $T_1$ or $T_2$ 
produced above. The swapping method is described below.

We choose to start from the spanning tree $T_1$ with $x_{min}$ edges. First, we pick a 
edge $e \in T_2 - T_1$ and the graph $T_1 \cup \{e\}$ contains a cycle $C$. Then 
the cycle must contain a edge $e' \notin T_2$. We form a new graph $T_1' = T_1 \cup 
\{e\} -\{e'\}$ and $T_1'$ has at least one edge belongs to $T_2$. Because $T_1$ can 
have at most $n-1$ edges different from $T_2$, namely $T_1$ and $T_2$ have no
common edge, therefore, after at most $n-1$ step mentioned above, $T_1$ will 
become $T_2$, and the number of X-edges in the spanning tree will be increased from
$x_{min}$ to $x_{max}$. In the process, each time only one edge is swapped, therefore
the number of X-edges in the spanning tree will increase at most 1. As a result, we can
get a exactly $k$ X-edges spanning tree during the swapping process.

The minimum spanning tree algorithm will take $O(m\log n)$. Each swapping will
take $O(m)$, and the whole swapping will take $O(mn)$. Therefore the total runtime
will be $O(mn)$

\section*{Question 3}
\paragraph*{a)}First, the general Resource Reservation Problem is NP, because, given any allocation schema, by checking each process whether its request is satisfied, we 
can tell whether there are $k$ active processes.

Second, we use independent set problem, and if we can show IS $\le_P$ RRP, then we 
can conclude that the general Resource Reservation Problem is NP-hard.

Given any arbitrary instance of independent set problem, where the graph is $G=(V, E)$
and the number of independent set is $k$, we will first construct an equivalent instance
of resource reservation problem. We let each node $v \in V$ denote one process, and
there is an edge $(u, v)$ if process $u$ and process $v$ both request at least one
common resource. If we can find a $k$-sized independent set in $G$, then the 
corresponding nodes are the active processes in resource reservation problem.
\begin{proof}
First, we prove ``$\Rightarrow$". When we have a $k$-sized independent set, we
have $k$ nodes are disjoint, namely $k$ processes request no common resources.
Therefore, these $k$ processes can be active.

Second, we prove ``$\Leftarrow$". When we have $k$ active processes, these 
processes will request no common resources at all. Then, in the corresponding graph
$G$, these $k$ nodes will have no edge between any two of them. Therefore, these
$k$ nodes form a $k$-sized independent set.
\end{proof}

Hereby, we have resource reservation problem is both NP and NP-hard, then we can 
conclude that resource reservation problem is NP-complete.

\paragraph*{b)}
\paragraph*{c)}
\paragraph*{d)}
\section*{Question 4}
\end{document}
